## Programming Assignment #2 Example

### Caching the Inverse of a Matrix
Matrix inversion is usually a costly computation and their may be some benefit to caching the inverse of a matrix rather than compute it repeatedly. This document demonstrates the use of special functions that cache the inverse of a matrix.

### Using base R Solve() function
First, we define a simple matrix
```{r}
my.matrix = matrix(c(1,2,2,1),nrow=2,ncol=2)
my.matrix
```
The inverse of a matrix is computed as follows:
```{r}
solve(my.matrix)
```

### Using "cacheable" inverse functions

#### makeCacheMatrix() function
This function creates a special "matrix" object that can cache its inverse.
``` {r}
source('cachematrix.R')
matrix.cached = makeCacheMatrix(my.matrix)
```
#### cacheSolve() function
This function creates a special "matrix" object that can cache its inverse.
``` {r}
cacheSolve(matrix.cached)
```

The second time the inverse is invoked, the cached version is used
``` {r}
cacheSolve(matrix.cached)
```


